---
title: "HW2Aisha"
output:
    html_document:
       keep_md: yes
---

# **HomeWork#2**

### Use the GEOmetabd package to find all HCV gene expression data
### use the Illumina platform submitted by an investigator at Yale. 

This should be done with a single query, showing the title, the GSE accession number, the GPL accession number and the manufacturer and the description of the platform used.




## Creating connection to GEOdatabase.
```{r,echo=TRUE}
source("http://bioconductor.org/biocLite.R")
biocLite()
biocLite(c("GEOmetadb", "GEOquery"))
```

##Load the library
```{r,echo=TRUE}
library(GEOmetadb)

```



```{r}
if(!file.exists("GEOmetadb.sqlite"))
{
  # Download database only if it's not done already
  getSQLiteFile()
}
```

##Finding data

```{r}
geo_con <-dbConnect(SQLite(),'GEOmetadb.sqlite')
dbListTables(geo_con)
dbListFields(geo_con,'gse_gpl')
dbListFields(geo_con, 'gsm')
dbListFields(geo_con, 'gse')
dbListFields(geo_con, 'gpl')

```


```{r}
res <- dbGetQuery(geo_con, "SELECT gse.title, gse.gse, gpl.ID, gpl.manufacturer,gpl.description FROM (gse JOIN gse_gpl ON gse.gse=gse_gpl.gse)j JOIN gpl ON j.gpl=gpl.gpl  WHERE gse.Title LIKE '%HCV%' AND gpl.Title LIKE '%Illumina%' AND gse.contact LIKE '%Institute: Yale %' ")
res
```
 

##Using data table, find the data and produce the result in one code. 


I tried different data table formate  since I failed on my first attempt 
```{r}
library(data.table)    
gse.dt <-data.table(dbGetQuery(geo_con,"SELECT * FROM gse"))
gse_gpl.dt <-data.table(dbGetQuery(geo_con,"SELECT * FROM gse_gpl"))
gpl.dt <-data.table(dbGetQuery(geo_con,"SELECT * FROM gpl"))

setkey(gse.dt,gse)
setkey(gse_gpl.dt,gse)
merge1<-merge(gse.dt,gse_gpl.dt)

setkey(merge1,gpl)
setkey(gpl.dt,gpl)
merge2<-merge(merge1,gpl.dt)
```

```{r}
merge2[title.x %like% "HCV" & contact.x %like% "Yale"& manufacturer %like% "Illumina",list(gse,gpl,manufacturer,description)]
```

